---
title: "p8105_hw3_jf3286.Rmd"
author: "Jingyu Fu"
date: "2019/10/13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)




library(ggridges)
library(patchwork)
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```




## Prob 1

load data from website
```{r}
library(p8105.datasets)
data("instacart")
```

Description: 

This data has `r ncolinstacart()` columns and`r nrow(instacart)`rows. It contains numeric columns and character columns. Overall, this data contains inforation about order ID, product ID, customer ID, aisle name, the number of products, the number of order, etc. The key variables are those including ID information, beucase these variables are unique to each order or user. From this data we can tell what has a certain customer purchased. For example, we can tell thet user ID 112108 purchased Bulgarian Yogurt, Organic 4% Milk Fat Whole Milk Cottage Cheese, Organic Celery Hearts, and other 5 types of product. We can also tell how many times a certain customer has ordered a product. For example, user ID 112108 ordered Bulgarian Yogurt twice, becuase it is shown in caolumn of reordered that it has been reordered once. 


Number of aisle
```{r}

  instacart%>% 
  group_by (aisle) %>%
  summarize (
    n_aisle = n()
    )
```

Aisle that are most items ordered from
```{r}
 instacart_n_items = instacart %>% 
  group_by(aisle) %>%
  summarize (
    n_items = sum(add_to_cart_order)
  ) 

  instacart_n_items %>%  mutate(
    rank_items = rank(n_items)
  ) %>% 
  filter (
    rank_items == 1
  )
  
```

Comments

Most items are ordered from aisle specialty wines champagnes, it can be assumed that among those investigated aisles in this data, specialty wines champagnes is the most popular aisle. 



Making plots,limiting to aisles with more than 10000 items, arranging aisles, and organizing plots
```{r}
instacart_n_items %>% 
  filter(
    n_items >= 10000
    ) %>% 
   mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n_items)
  ) %>% 
  ggplot(aes (x = aisle, y = n_items, color ="blue")) + 
  geom_point(alpha = .5) + 
  labs(
    title = "Aisle and number of items ordered",
    x = "Aisle",
    y = "Nuber of items ordered",
    caption = "Data from instcart"
  ) +
  theme_bw()+
  theme(legend.position = "bottom")+
  viridis::scale_color_viridis(
    name = "Aisle", 
    discrete = TRUE
  )

```

Comments

The plots look like a function graph. The number of items ordered from each ailse increased steadily at first but then there's a sudden  severe increase. For most of the aisles, each has  10110 ~ (5e^5)/2 items ordered, but for several others, there are a lot more.  


Making tables showing the three most popular items in each of the aisles
```{r}
instacart %>% 
  group_by(aisle) %>% 
  mutate(
    add_to_cart_order = desc(add_to_cart_order),
    rank_product = min_rank(add_to_cart_order)
  ) %>% 
  filter(
    rank_product == 1,2,3
  ) %>% 
  select(aisle, rank_product, product_name, add_to_cart_order) %>% 
   knitr::kable()
  
```
Comments

Each aisle has its own most popular items. For example, the most popular item in aisle dog food care is sausage cuts real beef treats. The order number of the most popular items in each aisle is around 60 to 80. 



Making table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week.
```{r}
instacart_2products = instacart %>%
  group_by(product_name,order_dow) %>% 
  filter(
    product_name %in%  c("Pink Lady Apples","Coffee Ice Cream")  
    )  %>% 
  summarize(
    mean_hour = mean(order_hour_of_day)
     
  ) %>% 
  pivot_wider (
    names_from = order_dow,
    values_from = mean_hour
  )
 
instacart_2products    
  
```

Comments
Coffee Ice Cream has its highest mean order hour of the day on order_dow 2(which is Monday), while Pink Lady Apples has its highest mean order hour of the day on order_dow 3 (which is Tuesday). 


## Problem 2

Load data from a package, and  do some data cleaning:

```{r}
library(p8105.datasets)
data("brfss_smart2010")

brfss_smart2010 = brfss_smart2010 %>% 
janitor::clean_names() %>% 
  rename (
    state = locationabbr ,
    county = locationdesc  
  ) %>% 
  filter(
    topic == "Overall Health", 
   response %in% c("Poor", "Fair", "Good", "Very good", "Excellent")
           ) %>% 
  mutate (
    response = factor(response),
    response = fct_relevel (response, "Poor", "Fair", "Good", "Very good", "Excellent")
  )

```

In 2002 and 2010, finding the states that were observed at 7 or more locations.
```{r}
brfss_smart2010 %>% 
  group_by(state) %>% 
  filter(year == 2002) %>% 
  summarize (
    n_location = n_distinct(county)
  ) %>% 
    filter(n_location >= 7)
  
brfss_smart2010 %>% 
  group_by(state) %>% 
  filter(year == 2010) %>% 
  summarize (
    n_location = n_distinct(county)
  ) %>% 
    filter(n_location >= 7)
```
Comments
In 2002, there are 6 states that were observed at 7 or more locations, while in 2010, there were 14. States including FL, MA, NC, NJ, PA were both observed in 2002 and 2010. 


Construct a dataset that is limited to Excellent responses, and contains, year, state, and a Make a “spaghetti” plot of this average value over time within a state. 

```{r}
dataset_prob2 = brfss_smart2010 %>% 
  group_by(state,year) %>% 
  filter (response == "Excellent") %>% 
  mutate (ave_data_value = mean (data_value)) %>% 
  select (year, state, ave_data_value) 

 dataset_prob2 %>%
  ggplot()+
  geom_line( aes (x = year, y = ave_data_value, color = state),alpha = .5)+
   labs (
     title = "State and Year",
     x = "Year",
     y = "Average value",
     caption = "Data from BRFSS"
   )+
   theme_bw()+
   theme(legend.position = "bottom") +
   viridis::scale_color_viridis(
    name = "state", 
    discrete = TRUE
  )
 
 
```
Comments

For most those with a "Excellent" response, the average data value changes severely over time. For very few of them, the average value stays somewhere between 20 and 25, and most of them are between 15 and 30. 


Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}

plot_of_distribution = brfss_smart2010 %>% 
  group_by(response,year) %>% 
  filter(state == "NY" & year %in% c("2006","2010")  & response %in% c("Poor","Excellent")) %>% 
  ggplot(aes(x = county, y = data_value, color = response))+
  geom_col(aes(fill = response))+
  labs (
     title = "Distribution of data value among locations in 2006",
     x = "Locations",
     y = "Data value",
     caption = "Data from BRFSS"
   )+
   theme_bw()+
   theme(legend.position = "bottom")+
  facet_grid (~ year)+
  viridis::scale_color_viridis(
    name = "response", 
    discrete = TRUE)

plot_of_distribution
```
Comments

Those with a "Poor" response have a much higher data value compared to those with "Excellent" response. 





## Problem 3
Load, tidy, and otherwise wrangle the data.

```{r}
accel_data = read_csv(file = "./accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    day_of_week = case_when( 
      day == "Monday" ~ "Weekday",
      day == "Tuesday" ~ "Weekday",
      day == "Wednesday" ~ "Weekday",
      day == "Thursday" ~ "Weekday",
      day == "Friday" ~ "Weekday",
      day == "Saturday" ~ "Weekend",
      day == "Sunday" ~ "Weekend",
      TRUE ~ ""
      )
           ) %>% 
  select(week, day_id, day, day_of_week,everything())
```
Desicription
This data includes variables such as week, day_id, day, day_of_week and activity. There are 'r count(accel_data, week)'obervations for week. 





Aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. 
```{r}
accel_data_tra = accel_data %>% 
  group_by (day_id) %>% 
  pivot_longer(
    activity_1:activity_64,
    names_to = "activity_number",
    names_prefix = "activity_",
    values_to = "activity_counts"
  ) %>% 
  mutate(
    activity_total = sum(activity_counts) 
  ) %>% 
  select (week, day_id, day, day_of_week, activity_total)  
  
 accel_data_tra %>% 
  knitr::kable()
  
```
Comments(are any trends apparant?)

There is a general decreasing trend from Monday to Wednesday, but a sudden increase on Thursday, and then a general decreasing trend form Thursday to Sunday. 


Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r}
accel_data %>% 
  pivot_longer(
    activity_1:activity_64,
    names_to = "activity_number",
    names_prefix = "activity_",
    values_to = "activity_counts"
  ) %>% 
  ggplot(aes(x = activity_number, y = activity_counts, color = day)) +
  geom_point(alpha = .5)+
  labs(
    title = "24 hour activity timr courses",
    x = "time course",
    y = "activity counts",
    caption = "Data from accel data"
    
  )+
  theme_bw()+
  theme(legend.position = "bottom")
```
Description











